Fast and scalable Gaussian process modeling of stellar variability \vspace{-3\baselineskip}

### 2016-11-07 paper/ms.tex
working on CI

We derive a fast, $O(N)$, Gaussian Process approach that involves Lorentzian
kernels.  This basis set can approximate commonly used kernels, and is a good
description of stellar variability.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{kernel_approx.png}
\caption{Approximation of various kernels with the sums of damped cosines.
(a). Kernels that may be expressed exactly: constant (dark grey), exponential (cyan), 
cosine (olive), and damped cosine (salmon).
(b). Approximation of the squared-exponential (Gaussian) kernel (pink) with three
damped cosine kernels (magenta). (c). The approximation of the exponential-sine-squared
kernel with $\Gamma =1$ (blue) and $\Gamma = 3$ (green). (d). Two Mat\'ern kernels,
$K_{3/2}$ (yellow/brown) and $K_{5/2}$ (violet).  The Mat\'ern 3/2 kernel
is approximated with $b=100$. The exact kernels are solid, while approximate are dashed.}
\label{kernel_approx}
\end{center}
\end{figure}

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.175]{./twoterm.eps}
\hspace{0.2in}
\includegraphics[scale=1.0]{./colorcode.eps}
\end{center}
\caption{Pictorial description of the extended sparse matrix where $N=10$, $p_0=0$, and $p=2$, following
the example shown in \citet{Ambikasaran2015}.}
\label{matrix_structure}
\end{figure}

>>>>

We present a scalable method for Gaussian Process regression in one dimension
with a specific emphasis on large astronomical time-series data sets.
This method can be applied to any Gaussian Process model where the spectral
density can be expressed as any general mixture of Lorentzian functions.

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[width=\textwidth]{./approximate_kernels/kernel_approx.pdf}
\caption{Approximation of various kernels with the sums of damped cosines.
(a). Kernels that may be expressed exactly: constant (dark grey), exponential (cyan),
cosine (olive), and damped cosine (salmon).
(b). Approximation of the squared-exponential (Gaussian) kernel (pink) with three
damped cosine kernels (magenta). (c). The approximation of the exponential-sine-squared
kernel with $\Gamma =1$ (blue) and $\Gamma = 3$ (green). (d). Two Mat\'ern kernels,
$K_{3/2}$ (yellow/brown) and $K_{5/2}$ (violet).  The Mat\'ern 3/2 kernel
is approximated with $b=100$. The exact kernels are solid, while approximate are dashed.}
\label{kernel_approx}
\end{center}
\end{figure}

@@

\begin{figure}[!htbp]
\begin{center}
\includegraphics[scale=0.175]{./twoterm.pdf}
\hspace{0.2in}
\includegraphics[scale=1.0]{./colorcode.pdf}
\end{center}
\caption{Pictorial description of the extended sparse matrix where $N=10$, $p_0=0$, and $p=2$, following
the example shown in \citet{Ambikasaran2015}.}
\label{matrix_structure}
\end{figure}
